
%------------------------ P U B L I C A T I O N S -----------------------------|

\small
\bibliographystyle{plain}
\begin{thebibliography}{99}

\subsection*{Thèses}

\bibitem{hdr}
\textbf{Stéphane Genaud}.
\newblock 
{\em Exécutions de programmes parallèles à passage de messages sur grille de 
calcul}.
\newblock 
Habilitation à diriger des recherches de l'université Henri Poincaré, 
Nancy. Décembre 2009.
\newblock 
Rapporteurs : C. Cérin (Paris 13), F. Desprez (INRIA Rhônes-Alpes), 
T. Priol (INRIA Bretagne-Atlantique).\\[2mm]

\bibitem{icps-1997-4}
\textbf{Stéphane Genaud}.
\newblock {\em Transformations de programmes \textsc{Pei} : applications au
  parallélisme de données}.
\newblock Thèse de doctorat de l'université Louis Pasteur, Strasbourg, Janvier 1997.
\newblock Rapporteurs : Luc Bougé et Patrice Quinton. 

\subsection*{Chapitre de livre}

\bibitem{icps-book}
\textbf{Stéphane Genaud} et Choopan Rattanapoka.
\newblock 
\emph{A Peer-to-Peer Framework for Message Passing Parallel Programs.}
\newblock 
Parallel Programming and Applications in Grid, P2P and Network-based System,
in {\em Advances In Parallel Computing} Series. Editor G. R. Joubert.
IOS Press, juin 2009. 
 

\subsection*{Articles en revues internationales}

\setlength{\itemsep}{1.5mm}

\bibitem{icps-2016-fgcs}
\newblock Etienne Michon, Julien Gossa, \textbf{Stéphane Genaud}, Léo Unbekandt, et Vincent Kherbache.
\newblock Schlouder: a broker for IaaS clouds
\newblock {\em Future Generation Computer Systems}, Elsevier, Future Generation Comp. Syst. 69: 11-23 (2017), sept 2016.


\bibitem{icps-2015-ijcc}
\newblock Marc Frincû, \textbf{Stéphane Genaud} et Julien Gossa.
\newblock Client-Side Resource Management on the Cloud: Survey and Future Directions.
\newblock {\em International Journal of Cloud Computing}, Inderscience, 4(3), octobre 2015.


\bibitem{icps-2014-fgg-computer}
\newblock Marc Frincû, \textbf{Stéphane Genaud} et Julien Gossa.
\newblock On the efficiency of several VM provisioning strategies for workflows
with multi-threaded tasks on clouds.
\newblock {\em Computing}, Springer, published online, juin 2014.

%@article{
%year={2014},
%issn={0010-485X},
%journal={Computing},
%doi={10.1007/s00607-014-0410-0},
%title={On the efficiency of several VM provisioning strategies for workflows with multi-threaded tasks on clouds},
%url={http://dx.doi.org/10.1007/s00607-014-0410-0},
%publisher={Springer Vienna},
%keywords={Workflow scheduling; Virtual machine provisioning; Cloud computing; Cost and makespan modeling; 68M14; 68M20},
%author={Frincu, MarcE. and Genaud, Stéphane and Gossa, Julien},
%pages={1-28},
%language={English}
%}


\bibitem{icps-2009-217}
\newblock \textbf{Stéphane Genaud}, Emmanuel Jeannot et Choopan Rattanapoka.
\newblock Fault-Management in P2P-MPI.
\newblock {\em International Journal of Parallel Programming}, Springer, 
37(5):433--461, août 2009.


\bibitem{icps-2008-188}
\textbf{Stéphane Genaud}, Pierre Gançarski, Guillaume Latu, Alexandre Blansché, 
Choopan Rattanapoka et Damien Vouriot. \newblock Exploitation of a parallel 
clustering algorithm on commodity hardware with P2P-MPI.
\newblock 
{\em The Journal of SuperComputing}, Springer, 43(1):21--41, jan. 2008.


\bibitem{icps-2007-182}
\textbf{Stéphane Genaud} et Choopan Rattanapoka.
\newblock P2P-MPI: A Peer-to-Peer Framework for Robust Execution of Message 
Passing Parallel Programs on Grids.
\newblock {\em Journal of Grid Computing}, Springer, 5(1):27--42, mai 2007.


\bibitem{icps-2004-125}
\textbf{Stéphane Genaud}, Arnaud Giersch, et Frédéric Vivien.
\newblock Load-balancing scatter operations for Grid computing.
\newblock {\em Parallel Computing}, Elsevier, 30(8):923--946, août 2004.

\bibitem{icps-2004-107}
Marc Grunberg, \textbf{Stéphane Genaud} et Catherine Mongenet.
\newblock Seismic ray-tracing and Earth mesh modeling on various parallel
  architectures.
\newblock 
{\em The Journal of Supercomputing}, Kluwer, 29(1):27--44, juillet 2004.


\subsection*{Articles en revues nationales}
\bibitem{icps-2005-146}
\textbf{Stéphane Genaud} et Marc Grunberg. 
\newblock  Calcul de rais en tomographie sismique : exploitation sur la grille.
\newblock {\em Technique et Science Informatiques}, numéro spécial Renpar, 
Hermès-Lavoisier, 24(5), pages 591--608, décembre 2005.

\bibitem{icps-1996-2}
\textbf{Stéphane Genaud}.
\newblock Transformations d'énoncés \textsc{Pei}.
\newblock {\em Technique et Science Informatiques}, 15(5), pages 601--618, 
Hermès, avril 1996.


\subsection*{Conférences internationales avec actes et comité de lecture}

\bibitem{icps-europar-2018}
Luke Bertot, Stéphane Genaud, Julien Gossa.
\newblock Improving Cloud Simulation Using the Monte-Carlo Method. Euro-Par 2018.
\newblock Euro-Par, Turin, Italy, Springer, LNCS, sept. 2018 

\bibitem{icps-ccgrid-2018}
Luke Bertot, Stéphane Genaud, Julien Gossa:
\newblock An Overview of Cloud Simulation Enhancement Using the Monte-Carlo Method. 
\newblock CCGrid, Washington, mai 2018.



\bibitem{icps-europar-2015}
Matthieu Kuhn, Guillaume Latu, Nicolas Crouseilles et \textbf{Stéphane Genaud}
\newblock Parallelization of an advection-diffusion problem arising in edge plasma physics using hybrid MPI/OpenMP programming.
\newblock Euro-Par, Vienne, Austria, Springer, LNCS, janvier 2015.

\bibitem{smpi13}  Paul  Bédaride,  Augustin Degomme,  \textbf{Stéphane  Genaud},
  Arnaud  Legrand,  George  S.  Markomanolis, Martin  Quinson,  Mark  Stillwell,
  Frederic Suter  and Brice Videau.   
\newblock Toward Better Simulation  of MPI
  Applications on  Ethernet/TCP Networks.  
\newblock 4th  International Workshop
  on  Performance  Modeling, Benchmarking  and  Simulation  of high  performance
  computing  systems,  part  of  SuperComputing   13.  Denver,  USA,  nov  2013.
\newblock \small{\textit{(taux: 30\%)}}

\bibitem{MichonGGFB13}
Etienne Michon, Julien Gossa, \textbf{Stéphane Genaud}, Marc Frincu and Alexandre Burel.
\newblock Porting Grid applications to the Cloud with Schlouder.
\newblock 5th IEEE International Conference on Cloud Computing Technology and Science (CloudCom 2013). Bristol, UK, dec 2013.
\newblock \small{\textit{(papiers acceptés/soumis{:}337/60(+34), taux: 17.8\%)}}

\bibitem{KuhnLGC13}
Matthieu Kuhn, Guillaume Latu, Stéphane Genaud and Nicolas Crouseilles.
\newblock Optimization and parallelization of Emedge3D on shared memory architecture.
\newblock HPCSP 2013: Workshop on HPC for Scientific Problems, Timisoara, Romania, sept 2013.


\bibitem{FrincuGG13}
Marc Frincu, \textbf{Stéphane Genaud} et Julien Gossa.
\newblock Comparing Provisioning and Scheduling Strategies for Workflows on Clouds
\newblock {\em 2nd IEEE International Workshop on Workflow Models, Systems, Services
and Applications in the Cloud (CloudFlow), IPDPS 2013}, mai 2013.

\bibitem{michon2012}
Etienne Michon, Julien Gossa, \textbf{Stéphane Genaud}.
\newblock Free elasticity and free CPU power for scientific workloads on IaaS Clouds
\newblock {\em 18th IEEE International Conference on Parallel and Distributed Systems}, 
IEEE, déc. 2012.
\newblock \small{\textit{(papiers acceptés/soumis:87/294, taux: 29\%)}}


\bibitem{icps-2011-225}
\newblock \textbf{Stéphane Genaud} et Julien Gossa,
\newblock Cost-wait Trade-offs in Client-side Resource Provisioning with 
Elastic Clouds.
\newblock {\em 4th IEEE International Conference on Cloud Computing (CLOUD 
2011)}, juillet 2011.
\newblock \small{\textit{(papiers acceptés/soumis{:}36/198, taux: 18\%)}}


\bibitem{icps-2011-224}
\newblock Pierre-Nicolas Clauss, Mark Stillwell, \textbf{Stéphane Genaud}, 
Fr\'ed\'eric Suter, Henri Casanova and  Martin Quinson.
\newblock Single Node On-Line Simulation of MPI Applications with SMPI.
\newblock {\em 25th IEEE International Parallel \& Distributed Processing 
Symposium (IPDPS 2011)}, mai 2011.
\newblock \small{\textit{(papiers acceptés/soumis{:}112/571, taux: 19\%)}}

\bibitem{icps-2009-219}
\newblock Virginie Galtier, \textbf{Stéphane Genaud} et Stéphane Vialle.
\newblock Implementation of the AdaBoost Algorithm for Large Scale Distributed 
Environments: Comparing JavaSpace and MPJ.
\newblock {\em 15th IEEE International Conference on Parallel and Distributed Systems}, 
IEEE, déc. 2009.
\newblock \small{\textit{(papiers acceptés/soumis:91/305, taux: 29\%)}}


\bibitem{icps-2009-214}
\textbf{Stéphane Genaud} and Choopan Rattanapoka.
\newblock Evaluation of Replication and Fault Detection in P2P-MPI.
\newblock 
{\em 6th IEEE International Workshop on Grid Computing (HPGC), IPDPS 2009}, 
mai 2009.
\newblock \textit{(Papier invité)}.

\bibitem{icps-2008-193}
\textbf{Stéphane Genaud} and Choopan Rattanapoka. 
\newblock Large-Scale Experiment of Co-allocation Strategies for Peer-to-Peer 
Supercomputing in P2P-MPI,
\newblock 
{\em 5th IEEE International Workshop on Grid Computing (HPGC), IPDPS 2008}, 
avril 2008.

\bibitem{icps-2007-192}
Ludovic Hablot and Olivier Glück and Jean-Christophe Mignot and \textbf{Stéphane Genaud} and Pascale Vicat-Blanc Primet.
\newblock Comparison and tuning of MPI implementation in a grid context.
\newblock {\em Proceedings of 2007 IEEE International Conference on Cluster Computing (CLUSTER)}, 458--463, september 2007.
\newblock \small{\textit{(papiers acceptés/soumis:42/106, taux: 39\%)}}

\bibitem{icps-2007-185}
\newblock \textbf{Stéphane Genaud} et Choopan Rattanapoka.
\newblock Fault Management in {\pmpi}. 
\newblock International Conference on {\em Grid and Pervasive Computing, 
(GPC 2007)}, LNCS, Springer, mai 2007.
\newblock \small{\textit{(papiers acceptés/soumis:56/217, taux: 25\%)}}
%submitted papers: 217; accepted : 56 full papers, 12 oral-short papers;  acceptance rate: 25\%

\bibitem{icps-2007-184}
\newblock \textbf{Stéphane Genaud}, Marc Grunberg et Catherine Mongenet.
\newblock Experiments in running a scientific {MPI} Application on GRID'5000. 
\newblock distingué par le \textsc{Intel} \textit{best paper award}.
\newblock {\em 4th IEEE International Workshop on Grid Computing (HPGC), IPDPS 
2007}, mars 2007.


\bibitem{icps-2005-155}
\textbf{Stéphane Genaud} et Choopan Rattanapoka.
\newblock A Peer-to-peer Framework for Robust Execution of Message Passing 
Parallel Programs.
\newblock 
In {\em EuroPVM/MPI 2005}, LNCS 3666, Springer-Verlag, pages 276--284, 
septembre 2005.
\newblock \small{\textit{(papiers acceptés/soumis:61/126, taux: 48\%)}}


\bibitem{icps-2004-124}
Marc Grunberg, \textbf{Stéphane Genaud}, et Catherine Mongenet.
\newblock Parallel adaptive mesh coarsening for seismic tomography.
\newblock In {\em SBAC-PAD 2004, 16th Symposium on Computer Architecture and
  High Performance Computing}. IEEE Computer Society Press, octobre 2004.
\newblock \small{\textit{(papiers acceptés/soumis:32/93, taux: 34\%)}}

\bibitem{icps-2003-75}
\textbf{Stéphane Genaud}, Arnaud Giersch, et Frédéric Vivien.
\newblock Load-balancing scatter operations for Grid computing.
\newblock In {\em Proceedings of 12th Heterogeneous Computing Workshop 
(HCW), IPDPS 2003}. IEEE Computer Society Press, avril 2003.

\bibitem{icps-2002-62}
Romaric David, \textbf{Stéphane Genaud}, Arnaud Giersch, \'{E}ric Violard, et 
  Benjamin Schwarz.
\newblock Source-code transformations strategies to load-balance Grid
  applications.
\newblock In {\em International Conference on Grid Computing - GRID'2002}, 
LNCS 2536, pages 82--87. Springer-Verlag, novembre 2002.

\bibitem{icps-2002-20}
Marc Grunberg, \textbf{Stéphane Genaud}, et Catherine Mongenet.
\newblock Parallel seismic ray-tracing in a global {E}arth mesh.
\newblock In {\em Proceedings of the 2002 Parallel and Distributed Processing
  Techniques and Applications (PDPTA'02)}, pages 1151--1157, juin 2002.

\bibitem{icps-1997-3}
Eric Violard, \textbf{Stéphane Genaud} et Guy-René Perrin.
\newblock Refinement of data-parallel programs in pei.
\newblock In {\em IFIP Working Conference on Algorithmic Language and Calculi}, 
R.~Bird and L.~Meertens editors, Chapman \& Hall~Ed., février 1997.
\newblock 25 pages.

\bibitem{icps-1995-1}
\textbf{Stéphane Genaud}, Eric Violard, et Guy-René Perrin.
\newblock Transformation techniques in \textsc{Pei}.
\newblock In P.~Magnusson S.~Haridi, K.~Ali, editor, {\em Europar'95}, LNCS
  966, pages 131--142. Springer-Verlag, août 1995.
\newblock \small{\textit{(papiers acceptés/soumis:50/180, taux: 27\%)}}




\subsection*{Conférences nationales avec actes et comité de lecture}
\bibitem{icps-2003-111}
Marc Grunberg et \textbf{Stéphane Genaud}.
\newblock Calcul de rais en tomographie sismique : exploitation sur la grille.
\newblock In {\em Renpar2003}, pages 179--186. INRIA, octobre 2003.

\bibitem{icps-1995-6}
\textbf{Stéphane Genaud}.
\newblock Techniques de tranformations d'énoncés \textsc{Pei} pour la
  production de programmes data-parallèles.
\newblock In {\em RenPar 7}, mai 1995, Mons, Belgique.

\bibitem{icps-1994-46}
Guy-René Perrin, Eric Violard et \textbf{Stéphane Genaud}.
\newblock \textsc{Pei} : a theoretical framework for data-parallel programming.
\newblock In {\em Workshop on Data-Parallel Languages and Compilers}, Lille, 
mai 1994.
\vspace{3mm}


\subsection*{Autres communications}

\bibitem{iphc-2011}
Christine Carapito, Jérôme Pansanel, Patrick Guterl, Alexandre Burel, Fabrice 
Bertile, \textbf{Stéphane Genaud}, Alain Van Dorsselaer, Christelle Roy.
\newblock Une suite logicielle pour la protéomique interfacée sur une grille de 
calcul. Utilisation d'algorithmes libres pour l'identification MS/MS, le 
séquençage de novo et l'annotation fonctionnelle.
\newblock Rencontres Scientifiques France Grilles 2011, Lyon.


\bibitem{ketterlin11}
Alain Ketterlin, \textbf{Stéphane Genaud}, Matthieu Kuhn.
\newblock Loop-Nest Recognition for the Extraction of Communication Patterns 
and the Compression of Message-Passing Parallel Traces.
\newblock Research Report ICPS 11-01. Université de Strasbourg. déc. 2011.


\bibitem{cds-2005}
A. Schaaff, F. Bonnarel, J.-J. Claudon, R. David, \textbf{S. Genaud}, M. Louys, 
C. Pestel and C. Wolf.
\newblock Work around distributed image processing and workflow management, 
\newblock ADASS 2005, Madrid.


\bibitem{icps-2003-113}
Marc Grunberg, \textbf{Stéphane Genaud}, et Michel Granet.
\newblock Geographical {ISC} data characterization with parallel ray-tracing.
\newblock In {\em Eos Trans. AGU, 84(46), Fall-Meeting Suppl., Abstract
  S31E-0793}, décembre 2003.

\end{thebibliography}
